Matching Bullets

### 2015-11-28 imaging-paper.Rnw
Produce the figure

\begin{figure}
<<fixedX, dependson='data', echo=FALSE, warning=FALSE, message=FALSE, fig.height=2, fig.width=6, out.width='\\linewidth'>>=
library(RColorBrewer)
library(ggplot2)
library(scales)
library(dplyr)
library(x3pr)
library(x3prplus)
library(grid)
library(gridExtra)
library(zoo)

@@

<<loess_step12, echo=FALSE, fig.width=10, fig.height=7, out.width='\\linewidth', warning=FALSE, fig.cap='Steps 1 and 2 of the Loess fit algorithm. The top panel is a plot of height values for part 1 of bullet 1 across different values of y, with x held constant at 243.75. The bottom panel is the same plot, but with the first and last 100 y values trimmed.', fig.pos='H', message=FALSE>>=
br111_bullet <- get_bullet(paste(datadir,"Br1 Bullet 1-1.x3p", sep = "/"))
br112_bullet <- get_bullet(paste(datadir,"Br1 Bullet 1-2.x3p", sep = "/"))
br113_bullet <- get_bullet(paste(datadir,"Br1 Bullet 1-3.x3p", sep = "/"))
br114_bullet <- get_bullet(paste(datadir,"Br1 Bullet 1-4.x3p", sep = "/"))
br115_bullet <- get_bullet(paste(datadir,"Br1 Bullet 1-5.x3p", sep = "/"))
br116_bullet <- get_bullet(paste(datadir,"Br1 Bullet 1-6.x3p", sep = "/"))

@@

<<loessfits, echo=FALSE, fig.width=10, fig.height=7, out.width='\\linewidth', warning=FALSE>>=
br111.groove <- get_grooves(br111_bullet)
br112.groove <- get_grooves(br112_bullet)
br113.groove <- get_grooves(br113_bullet)
br114.groove <- get_grooves(br114_bullet)
br115.groove <- get_grooves(br115_bullet)
br116.groove <- get_grooves(br116_bullet)

my.loess1 <- fit_loess(br111_bullet, br111.groove)
my.loess2 <- fit_loess(br112_bullet, br112.groove)
my.loess3 <- fit_loess(br113_bullet, br113.groove)
my.loess4 <- fit_loess(br114_bullet, br114.groove)
my.loess5 <- fit_loess(br115_bullet, br115.groove)
my.loess6 <- fit_loess(br116_bullet, br116.groove)

qplot(y, resid, data=subset(db2, x == 100), #colour=factor(x), 
      geom="line", size=I(1), colour=I("grey30")) + 
  facet_wrap(~part) + scale_colour_brewer(palette="Paired") +
  theme_bw() + theme(legend.position="bottom") + 
  geom_line(aes(y, resid, group =x), colour="black", size=1, alpha=0.2, 
             data = filter(db1, part==2, x == 100)[,c("y", "resid", "x")]) + ggtitle("Part 2 of Bullet 1 in black")
@

>>>>

\begin{figure}
<<fixedX, dependson='data', echo=FALSE, warning=FALSE, message=FALSE, fig.height=2, fig.width=6, out.width='\\linewidth'>>=
library(RColorBrewer)
library(ggplot2)
library(scales)
library(dplyr)
library(x3pr)
library(x3prplus)
library(grid)
library(gridExtra)
library(zoo)
library(tidyr)

@@

<<loess_step12, echo=FALSE, fig.width=10, fig.height=7, out.width='\\linewidth', warning=FALSE, fig.cap='Steps 1 and 2 of the Loess fit algorithm. The top panel is a plot of height values for part 1 of bullet 1 across different values of y, with x held constant at 243.75. The bottom panel is the same plot, but with the first and last 100 y values trimmed.', fig.pos='H', message=FALSE>>=
br111_bullet <- get_bullet(paste(datadir,"Br1 Bullet 1-1.x3p", sep = "/"))

br121_bullet <- get_bullet(paste(datadir,"Br1 Bullet 2-1.x3p", sep = "/"))
br122_bullet <- get_bullet(paste(datadir,"Br1 Bullet 2-2.x3p", sep = "/"))
br123_bullet <- get_bullet(paste(datadir,"Br1 Bullet 2-3.x3p", sep = "/"))
br124_bullet <- get_bullet(paste(datadir,"Br1 Bullet 2-4.x3p", sep = "/"))
br125_bullet <- get_bullet(paste(datadir,"Br1 Bullet 2-5.x3p", sep = "/"))
br126_bullet <- get_bullet(paste(datadir,"Br1 Bullet 2-6.x3p", sep = "/"))

@@

We can reproduce a similar figure to the one from the circular fits by overlaying the residuals from each loess fit for bullet 2 onto an image of the loess residuals from part 1 of bullet 1. This is available in Figure \ref{fig:loessfits}.

<<loessfits, echo=FALSE, fig.width=10, fig.height=7, out.width='\\linewidth', warning=FALSE>>=
br121.groove <- get_grooves(br121_bullet)
br122.groove <- get_grooves(br122_bullet)
br123.groove <- get_grooves(br123_bullet)
br124.groove <- get_grooves(br124_bullet)
br125.groove <- get_grooves(br125_bullet)
br126.groove <- get_grooves(br126_bullet)

my.loess1 <- fit_loess(br121_bullet, br121.groove)
my.loess2 <- fit_loess(br122_bullet, br122.groove)
my.loess3 <- fit_loess(br123_bullet, br123.groove)
my.loess4 <- fit_loess(br124_bullet, br124.groove)
my.loess5 <- fit_loess(br125_bullet, br125.groove)
my.loess6 <- fit_loess(br126_bullet, br126.groove)

my.loessactual <- fit_loess(br111_bullet, br111.groove)

minrows <- min(length(my.loess1$data$resid),
               length(my.loess2$data$resid),
               length(my.loess3$data$resid),
               length(my.loess4$data$resid),
               length(my.loess5$data$resid),
               length(my.loess6$data$resid),
               length(my.loessactual$data$resid))

my.df <- data.frame(y = my.loess1$data$y[1:minrows], resid1 = my.loess1$data$resid[1:minrows],
                    resid2 = my.loess2$data$resid[1:minrows], resid3 = my.loess3$data$resid[1:minrows],
                    resid4 = my.loess4$data$resid[1:minrows], resid5 = my.loess5$data$resid[1:minrows],
                    resid6 = my.loess6$data$resid[1:minrows])

melt.df <- my.df %>%
    gather(key = part, value = resid, resid1:resid6)
melt.df$part <- gsub("resid", "", melt.df$part)

actual.df <- my.loessactual$data[1:minrows,]

qplot(y, resid, data=melt.df, #colour=factor(x), 
      geom="line", size=I(1), colour=I("grey30")) + 
  facet_wrap(~part) + scale_colour_brewer(palette="Paired") +
  theme_bw() + theme(legend.position="bottom") + 
  geom_line(data = actual.df, aes(y, resid), colour="black", size=1, alpha=0.2) + ggtitle("Part 1 of Bullet 1 in black")
@
